Black swans in ecological time series\\ Black swans in population dynamics\\ Heavy-tailed ecological time series\\ Black swans in ecological dynamics\\ Black swan ecological dynamics\\ \ldots

### 2016-11-17 analysis/cause-table.tex
Update output tables

% latex table generated in R 3.2.0 by xtable 1.7-4 package

@@

\includegraphics[width=1.7cm]{../analysis/sparks/6528.pdf} & Shag, \textit{Phalacrocorax aristotelis}, Farne Islands, Northumberland & 6528 & \cite{potts1980} & Red tide event combined with low productivity due to overcrowding & 1.00 \\ 
  \includegraphics[width=1.7cm]{../analysis/sparks/7115.pdf} & South African fur seal, \textit{Arctocephalus pusillus}, South Africa & 7115 & \cite{shaughnessy1982} & Harvesting and predation changes & 1.00 \\ 
  \includegraphics[width=1.7cm]{../analysis/sparks/10128.pdf} & Red grouse, \textit{Lagopus lagopus scoticus}, Scotland - un-named area & 10128 & \cite{potts1984} & Environment- and parisite-caused cycles & 1.00 \\ 
  \includegraphics[width=1.7cm]{../analysis/sparks/9382.pdf} & Pine looper or Bordered white, \textit{Bupalus piniaria}, Kessock & 9382 & \cite{broekhuizen1993} & Unknown, but sampling intensity was decreasing & 1.00 \\ 
  \includegraphics[width=1.7cm]{../analysis/sparks/10127.pdf} & Red grouse, \textit{Lagopus lagopus scoticus}, Scotland - un-named area & 10127 & \cite{potts1984} & Environment- and parisite-caused cycles & 0.99 \\ 
  \includegraphics[width=1.7cm]{../analysis/sparks/10007.pdf} & Water vole, \textit{Arvicola terrestris}, Le Pont & 10007 & \cite{saucy1994} & Predator-environment cycle interactions & 1.00 \\ 
  \includegraphics[width=1.7cm]{../analysis/sparks/20579.pdf} & Grey heron, \textit{Ardea cinerea}, Southern Britain & 20579 & \cite{stafford1971} & Severe winter & 0.98 \\ 
  \includegraphics[width=1.7cm]{../analysis/sparks/9655.pdf} & Flea beetle, \textit{Chaetocnoma concinna}, Finland & 9655 & \cite{markkula1965} & Cannot locate original source & 0.99 \\ 
  \includegraphics[width=1.7cm]{../analysis/sparks/1235.pdf} & Wren, \textit{Troglodytes troglodytes}, Eastern Wood, Bookham Common & 1235 & \cite{newton1998} & Severe winter & 0.98 \\ 
  \includegraphics[width=1.7cm]{../analysis/sparks/10113.pdf} & Willow grouse, \textit{Lagopus lagopus}, Northern England & 10113 & \cite{dobson1995} & Parasites and predators & 0.99 \\ 
  \includegraphics[width=1.7cm]{../analysis/sparks/9667.pdf} & Gooseberry sawfly, \textit{Nemastus ribesii}, Finland & 9667 & \cite{markkula1965} & Cannot locate original source & 0.97 \\ 
  \includegraphics[width=1.7cm]{../analysis/sparks/9679.pdf} & Unknown, \textit{Trioza apicalis}, Finland & 9679 & \cite{markkula1965} & Cannot locate original source & 0.83 \\ 
  \includegraphics[width=1.7cm]{../analysis/sparks/20527.pdf} & Wandering albatross, \textit{Diomedea exulans}, Taiaroa & 20527 & \cite{robertson1998} & Unknown & 0.99 \\ 
  \includegraphics[width=1.7cm]{../analysis/sparks/10039.pdf} & Red grouse, \textit{Lagopus lagopus scoticus}, Northern Scotland & 10039 & \cite{dobson1995} & Parasites and predators & 0.92 \\ 
  \includegraphics[width=1.7cm]{../analysis/sparks/10162.pdf} & Red grouse, \textit{Lagopus lagopus scoticus}, Atholl Estate & 10162 & \cite{mackenzie1952} & Bad environmental conditions and overcrowding combined to create crashes & 0.91 \\ 
  \includegraphics[width=1.7cm]{../analysis/sparks/9503.pdf} & Fisher or  Pekan, \textit{Martes pennanti}, Manitoba & 9503 & \cite{keith1963} & Unknown & 0.76 \\ 
  \includegraphics[width=1.7cm]{../analysis/sparks/7099.pdf} & European rabbit, \textit{Oryctolagus cuniculus}, Estate 2, East Anglia & 7099 & \cite{barnes1986} & Disease outbreak followed by years of good weather & 0.78 \\ 
  \includegraphics[width=1.7cm]{../analysis/sparks/2778.pdf} & Wheatear, \textit{Oenanthe oenanthe}, Skokholm Island & 2778 & \cite{lack1969} & Unknown, but decline noted specifically, cold winters caused some crashes & 0.67 \\ 
  \includegraphics[width=1.7cm]{../analysis/sparks/1195.pdf} & Blue jay, \textit{Cyanocitta cristata}, Robert Allerton Park & 1195 & \cite{kendeigh1982} & Unknown & 0.60 \\ 
  \includegraphics[width=1.7cm]{../analysis/sparks/5019.pdf} & Barbary macaque, \textit{Macaca sylvanus}, Queens Gate & 5019 & \cite{fa1984} & Cannot locate original source & 0.61 \\ 

>>>>

% latex table generated in R 3.3.1 by xtable 1.8-2 package

@@

\includegraphics[width=1.7cm]{../analysis/sparks/6528.pdf} & Shag, \textit{Phalacrocorax aristotelis}, Farne Islands, Northumberland & 6528 & \citep{potts1980} & Red tide event combined with low productivity due to overcrowding & 1.00 \\ 
  \includegraphics[width=1.7cm]{../analysis/sparks/7115.pdf} & South African fur seal, \textit{Arctocephalus pusillus}, South Africa & 7115 & \citep{shaughnessy1982} & Harvesting and predation changes & 1.00 \\ 
  \includegraphics[width=1.7cm]{../analysis/sparks/9382.pdf} & Pine looper or Bordered white, \textit{Bupalus piniaria}, Kessock & 9382 & \citep{broekhuizen1993} & Unknown, but sampling intensity was decreasing & 1.00 \\ 
  \includegraphics[width=1.7cm]{../analysis/sparks/10127.pdf} & Red grouse, \textit{Lagopus lagopus scoticus}, Scotland - un-named area & 10127 & \citep{potts1984} & Environment- and parisite-caused cycles & 1.00 \\ 
  \includegraphics[width=1.7cm]{../analysis/sparks/10128.pdf} & Red grouse, \textit{Lagopus lagopus scoticus}, Scotland - un-named area & 10128 & \citep{potts1984} & Environment- and parisite-caused cycles & 1.00 \\ 
  \includegraphics[width=1.7cm]{../analysis/sparks/10007.pdf} & Water vole, \textit{Arvicola terrestris}, Le Pont & 10007 & \citep{saucy1994} & Predator-environment cycle interactions & 1.00 \\ 
  \includegraphics[width=1.7cm]{../analysis/sparks/20579.pdf} & Grey heron, \textit{Ardea cinerea}, Southern Britain & 20579 & \citep{stafford1971} & Severe winter & 0.99 \\ 
  \includegraphics[width=1.7cm]{../analysis/sparks/1235.pdf} & Wren, \textit{Troglodytes troglodytes}, Eastern Wood, Bookham Common & 1235 & \citep{newton1998} & Severe winter & 0.98 \\ 
  \includegraphics[width=1.7cm]{../analysis/sparks/9655.pdf} & Flea beetle, \textit{Chaetocnoma concinna}, Finland & 9655 & \citep{markkula1965} & Cannot locate original source & 0.99 \\ 
  \includegraphics[width=1.7cm]{../analysis/sparks/10113.pdf} & Willow grouse, \textit{Lagopus lagopus}, Northern England & 10113 & \citep{dobson1995} & Parasites and predators & 0.99 \\ 
  \includegraphics[width=1.7cm]{../analysis/sparks/9667.pdf} & Gooseberry sawfly, \textit{Nemastus ribesii}, Finland & 9667 & \citep{markkula1965} & Cannot locate original source & 0.97 \\ 
  \includegraphics[width=1.7cm]{../analysis/sparks/9679.pdf} & Unknown, \textit{Trioza apicalis}, Finland & 9679 & \citep{markkula1965} & Cannot locate original source & 0.85 \\ 
  \includegraphics[width=1.7cm]{../analysis/sparks/20527.pdf} & Wandering albatross, \textit{Diomedea exulans}, Taiaroa & 20527 & \citep{robertson1998} & Unknown & 1.00 \\ 
  \includegraphics[width=1.7cm]{../analysis/sparks/10039.pdf} & Red grouse, \textit{Lagopus lagopus scoticus}, Northern Scotland & 10039 & \citep{dobson1995} & Parasites and predators & 0.92 \\ 
  \includegraphics[width=1.7cm]{../analysis/sparks/10162.pdf} & Red grouse, \textit{Lagopus lagopus scoticus}, Atholl Estate & 10162 & \citet{mackenzie1952} & Bad environmental conditions and overcrowding combined to create crashes & 0.92 \\ 
  \includegraphics[width=1.7cm]{../analysis/sparks/7099.pdf} & European rabbit, \textit{Oryctolagus cuniculus}, Estate 2, East Anglia & 7099 & \citep{barnes1986} & Disease outbreak followed by years of good weather & 0.81 \\ 
  \includegraphics[width=1.7cm]{../analysis/sparks/9503.pdf} & Fisher or  Pekan, \textit{Martes pennanti}, Manitoba & 9503 & \citep{keith1963} & Unknown & 0.74 \\ 
  \includegraphics[width=1.7cm]{../analysis/sparks/2778.pdf} & Wheatear, \textit{Oenanthe oenanthe}, Skokholm Island & 2778 & \citep{lack1969} & Unknown, but decline noted specifically, cold winters caused some crashes & 0.68 \\ 
  \includegraphics[width=1.7cm]{../analysis/sparks/1195.pdf} & Blue jay, \textit{Cyanocitta cristata}, Robert Allerton Park & 1195 & \citep{kendeigh1982} & Unknown & 0.62 \\ 
  \includegraphics[width=1.7cm]{../analysis/sparks/9953.pdf} & Rock ptarmigan, \textit{Lagopus mutus}, Iceland & 9953 & \citep{clarke1885,williams1954} & Severe winters & 0.61 \\ 
